---
title: "Simple document"
author : "Sameera Reem"
output: 
html_document:
    toc: true
    toc_float: true
---

I'm an R Markdown document! 

# Section 0 : libraries
```{r echo = F, message = F} 
library(tidyverse)
```

#echo?
#echo vs message? echo hides code chunks and message hides general messages
#what is r eval?

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3 : a tibble
```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )
```

# Section 4 : plots
```{r}
ggplot(plot_df, aes(x=x)) + geom_histogram()

ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```

# Section 5 : Learning Assessment 2
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. 

This plot shows the distribution of the absolute value of 

```{r Assessment 2}
df = 
  tibble(
    num_var = rnorm(n=500, mean=1),
    vec_logical = num_var > 0,
    abs_var = abs(num_var)
  )

ggplot(df, aes(x=abs_var)) + geom_histogram()
```
The median is `r round(median(pull(df, num_var)), 2)`.


# Section 6 : Formatting
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7 : Learning Assessment 3
After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* The mean is `r round(mean(pull(df, num_var)), 2)`.
* The median is `r round(median(pull(df, num_var)), 2)`.
* The standard deviation is `r round(sd(pull(df, num_var)), 2)`.

#The asterisk puts it on different lines